### 2020-10-28 publications.tex
Update in October 2020

\begin{benumerate}{8}
\item \textit{Modeling UV Radiative Feedback from Massive Stars: III. Escape
    of Radiation from Star-Forming Giant Molecular Clouds} \\ \textbf{Kim,
    J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, \textit{ApJ accepted}
\item \textit{Modeling UV Radiative Feedback from Massive Stars: II. Dispersal
of Star-Forming Giant Molecular Clouds by Photoionization and Radiation
Pressure} \\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, ApJ, 859,
68
\item \textit{Modeling UV Radiative Feedback from Massive Stars: I.
Implementation of Adaptive Ray Tracing Method and Tests}\\ \textbf{Kim, J.-G.},
Kim, W.-T., Ostriker, E. C.,\& Skinner A. M. 2017, ApJ, 851, 93
\item \textit{Disruption of Molecular Clouds by Expansion of Dusty H II
Regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2016, ApJ, 819,
137
\item \textit{Instability of Magnetized Ionization Fronts Surrounding H II
regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T. 2014, ApJ, 797, 135
\item \textit{Nature of Wiggle Instability of Galactic Spiral Shocks}\\ Kim,
W.-T., Kim, Y., \& \textbf{Kim, J.-G.} 2014, ApJ, 789, 68
\item \textit{Instability of Evaporation Fronts in the Interstellar Medium}\\
  \textbf{Kim, J.-G.}, Kim, W.-T. 2013, ApJ, 779, 48
\item \textit{Gravitational Instability of Rotating, Pressure-Confined,
    Polytropic Gas Disks with Vertical Stratification} \\ \textbf{Kim, J.-G.},
  Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012, ApJ, 761, 131
\end{benumerate}

\subsection{Papers in Preparation}
\begin{enumerate}
\item[] \textit{Diffuse Ionized Gas in TIGRESS Simulations of the ISM}\\
  Kado-Fong, E., \textbf{Kim, J.-G.}, Kim, C.-G., \& Ostriker, E. C.
  \textit{2019, to be submitted}
\item[] \textit{Recovery of Cloud-Scale Star Formation Rate Based on Ionizing
    Luminosity: Calibration for Escape of Radiation} \\ \textbf{Kim, J.-G.} \&
  Ostriker, E. C. \textit{2019, in prep}
\item[] \textit{TIGRESS-RT: Implementation New Heating/Cooling Module with
    Adaptive Ray Tracing}\\ \textbf{Kim, J.-G.}, Gong, M., Kim, C.-G., \&
  Ostriker, E. C.
\end{enumerate}

>>>>

*Authored by students under direct supervision

\begin{benumerate}{11}
\item \textit{The environmental dependence of the $X_{\mathrm CO}$ conversion
    factor}\\ Gong, M., Ostriker, E. C., Kim, C.-G., \& \textbf{Kim,
    J.-G.}, \textit{ApJ accepted}
\item \textit{Factories of CO-dark gas: molecular clouds with limited star
formation efficiencies by far-ultraviolet feedback} \\
  Inoguchi, M., Hosokawa, T., Mineshige, S., \& \textbf{Kim, J.-G.} 2020, MNRAS,
  497, 5061I
\item \textit{Diffuse Ionized Gas in Simulations of Multiphase, Star-forming
    Galactic Disks}\\
  $^{*}$Kado-Fong, E., \textbf{Kim, J.-G.}, Ostriker, E. C., \& Kim, C.-G. 2020, ApJ,
  897, 143
\item \textit{Modeling UV Radiative Feedback from Massive Stars: III. Escape
    of Radiation from Star-Forming Giant Molecular Clouds} \\ \textbf{Kim,
    J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, ApJ, 883, 102
\item \textit{Modeling UV Radiative Feedback from Massive Stars: II. Dispersal
of Star-Forming Giant Molecular Clouds by Photoionization and Radiation
Pressure} \\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, ApJ, 859,
68
\item \textit{Modeling UV Radiative Feedback from Massive Stars: I.
Implementation of Adaptive Ray Tracing Method and Tests}\\ \textbf{Kim, J.-G.},
Kim, W.-T., Ostriker, E. C.,\& Skinner A. M. 2017, ApJ, 851, 93
\item \textit{Disruption of Molecular Clouds by Expansion of Dusty H II
Regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2016, ApJ, 819,
137
\item \textit{Instability of Magnetized Ionization Fronts Surrounding H II
regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T. 2014, ApJ, 797, 135
\item \textit{Nature of Wiggle Instability of Galactic Spiral Shocks}\\ Kim,
W.-T., Kim, Y., \& \textbf{Kim, J.-G.} 2014, ApJ, 789, 68
\item \textit{Instability of Evaporation Fronts in the Interstellar Medium}\\
  \textbf{Kim, J.-G.}, Kim, W.-T. 2013, ApJ, 779, 48
\item \textit{Gravitational Instability of Rotating, Pressure-Confined,
    Polytropic Gas Disks with Vertical Stratification} \\ \textbf{Kim, J.-G.},
  Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012, ApJ, 761, 131
\end{benumerate}

\subsection{Papers in Preparation}
\begin{enumerate}
\item[] \textit{Dispersal of Star-Forming Molecular Clouds by UV Radiation
    Feedback: Dependence on Gravitational Boundedness and Magnetic Fields} \\
  \textbf{Kim, J.-G.}, Ostriker, E. C., \& Filippova, N. \textit{2020, to be
    submitted}
\item[] \textit{Implementation of a Cooling Module for the ISM Coupled with Radiative
    Transfer}\\ \textbf{Kim, J.-G.}, Gong, M., Kim, C.-G., \& Ostriker, E. C.
  \textit{2020, to be submitted}
\item[] \textit{A Theory of Stellar Wind Bubble Expansion in the Turbulent
    ISM}\\
  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G.,
  \textit{2020, in preparation}
\item[] \textit{r-process Enrichment During the Formation of a Globular Cluster: Case
    of M15} \\
  Hotokezaka, K., \textbf{Kim, J.-G.}, Beniamini, P., \& Cen, R. \textit{2021,
    in preparation}

  % \item[] \textit{Recovery of Cloud-Scale Star Formation Rate Based on Ionizing
%     Luminosity: Calibration for Escape of Radiation} \\ \textbf{Kim, J.-G.} \&
%   Ostriker, E. C. \textit{2019, in prep}
\end{enumerate}
